Informing IPCC accounting of forest carbon using the global forest carbon database (ForC v4.0)

### 2023-05-08 doc/manuscript/ESSDmanuscript.Rmd
provide info on web scraping Citation #41
@teixeirak, I was not able to knit because the .rmd is looking for some file(s) in your machine. Let me know if what I edited provides enough detail.

We added or modified a total of `r n_fields_modified` fields (`r table_ForCchanges`).
Most notably, these included improvement of the representation of uncertainty, recording of original units and organic matter to C conversion factors, and expanding the information recorded in the citations table. 
For the latter, we *used an R script to automatically retrieve information based on the DOI ([issue 41](https://github.com/forc-db/IPCC-EFDB-integration/issues/41))*<!--needs info from Valentine here-->.

>>>>

We added or modified a total of `r n_fields_modified` fields (`r table_ForCchanges`).
Most notably, these included improvement of the representation of uncertainty, recording of original units and organic matter to C conversion factors, and expanding the information recorded in the citations table. 
For the latter, we used an R script to automatically harvest (scrape) the URL, citation, abstract and language of the publications, based on their DOI, using R package `rvest`[ @rvest]). That information was manually retrieved when the web scraping failed.
